\papertitle

### 2017-06-11 paper/paper.tex
Incorporated revisions, removed local maxima plotting of 2 component estimates.

\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subfig} % or can use subcaption package
\usepackage{color}
\usepackage{cite}

@@

% Flowchart drawing stuff
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\tikzstyle{startstop} = [rectangle,draw=black,text centered]%, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text
centered, draw=black, text width=3cm]
\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

%---------------TWO-AUTHOR HEADER STARTS (uncomment below if your paper has two authors)-----------------------
\twoaffiliations{
\paperauthorA \,}
{\href{http://www.cirmmt.org/}{%Sound Processing and Control Laboratory
        SPCL %
        \sthanks{Sound Processing and Control Laboratory} \\%
%        Centre for Interdisciplinary Research in Music Media and Technology
        CIRMMT %
        \sthanks{Centre for Interdisciplinary Research in Music Media and Technology}%
    }
\\ McGill University %
\\ Montreal, Quebec, Canada \\
{\tt \href{mailto:nicholas.esterer@mail.mcgill.ca}{nicholas.esterer@mail.mcgill.ca}}
}
{\paperauthorB \,}
{\href{http://www.cirmmt.org/}{%Sound Processing and Control Laboratory
        SPCL \\%
%        \sthanks{Sound Processing and Control Laboratory} \\%
%        Centre for Interdisciplinary Research in Music Media and Technology
        CIRMMT %
%        \sthanks{Centre for Interdisciplinary Research in Music Media and Technology}%
    } %
\\ McGill University %
\\ Montreal, Quebec, Canada \\
{\tt %
\href{mailto:philippe.depalle@mcgill.ca}{philippe.depalle@mcgill.ca}}
}

@@

The sinusoidal model typically considered is
%
\begin{equation}
    \label{eq:polyphaseexp}
    s(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j) + \eta(t)
\end{equation}
where $\eta(t)$ is white Gaussian noise.
%
Although this technique can be extended to describe a single sinusoid of
arbitrary complexity simply by increasing $Q$, it remains essential to consider
signals featuring a sum of $P$ such components, whether they represent the harmonic structure of a musical sound or the union of partials resulting from a mixture of multiple signal sources (e.g., recordings of multiple speakers or performers),  i.e., 
%
\begin{equation}
    \label{eq:polyphaseexpmix}
    x(t) = \sum_{i=1}^{P} x_{i}(t) + \eta(t)
\end{equation}
%
with
%
\[
    x_{i}(t) = \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j)
\]
%
As regards the design and evaluation of signal-derivatives analysis techniques,
previous work has generally assumed signals containing a single component, i.e.,
$P$ = 1 or assumed the influence of other components to be negligible. Later we
will refine when this assumption can be made. In \cite{hamilton2012comparisons}
the authors provide a comprehensive evaluation of various signal-derivatives
analysis methods applied to a single-component signal. In
\cite{robel2002estimating} the extent to which two components in mixture can
corrupt estimations of the frequency slope ($\Im\{a_{0,2}\}$ and
$\Im\{a_{1,2}\}$) is investigated in the context of the reassignment method, one
of the ``signal-derivatives'' techniques, but the corruption of the other
parameters is not considered.

In this paper, we revisit the quality of signal-derivatives estimation of
\textit{all} the $a_{j}$ when analyzing a \textit{mixture} of components. We focus on
the DDM \cite{betser2009sinusoidal} analysis method for its convenience as it
can simply be considered as an atomic decomposition (see
Sec.~\ref{sec:estimating_aj}), and does not require computing derivatives
of the signal to be analysed.

DDM does, however, require a once-differentiable analysis window. As we are
interested in windows with lower sidelobes in order to better estimate
parameters of sinusoidal chirp signals in mixture, we seek windows that
combine these two properties. For this, a technique to design
once-differentiable approximations to arbitrary symmetrical windows is proposed
and presented along with a design example for a high-performance window. Finally
we evaluate the performance of various once-differentiable windows in estimating
the $a_{j}$.

\section{Estimating the \lowercase{$a_{j}$}}
\label{sec:estimating_aj}
We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
the theory of distributions \cite{schwartz1959theorie}, the DDM
makes use of ``test
functions'' or atoms $\psi$. These atoms must be once differentiable with
respect to time variable $t$ and be non-zero only on a finite interval
$[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
%
\begin{equation}
    \label{eq:ddm:inner:prod:def}
    \left\langle x , \psi \right\rangle = 
    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
\end{equation}
%
and the operator 
%
\[
\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
\]
%
Consider the weighted signal
%
\[
    f(t) = x(t) \overline{\psi}(t)
\]
%
differentiating with respect to $t$ we obtain
%
\begin{multline}
    \label{eq:ddm:weighted:sig:derivative}
    \frac{df}{dt}(t) = 
    \frac{dx}{dt}(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t) = \\
    \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t)
\end{multline}
%
Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
$\frac{df}{dt}(t)$ we obtain
%
\begin{multline*}
    \int_{-\infty}^{\infty}\frac{df}{dt}(t)dt = \\
    \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
    + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
\end{multline*}
%
or, using the operator $\mathcal{T}^{\alpha}$,
%
\[ 
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
\]
%

Estimating coefficients $a_j$, ${1 < j \leq Q}$,
simply requires $R$ atoms with $R \geq Q$ to solve the linear system of
equations
\begin{equation}
    \label{eq:ddmsyseq}
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi}_{r} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dt} \right\rangle
\end{equation}
for $1 \leq r \leq R$.

To estimate $a_0$ we rewrite the signal we are analysing as
\[
    x(t) = \exp(a_0) \gamma(t) + \epsilon (t)
\]
where $\epsilon (t)$ is the error signal, the part of the signal that is not explained
by our model, and $\gamma (t)$ is the part of the signal
whose coefficients have already been estimated, i.e.,
\[
    \gamma(t) = \exp \left( \sum_{j=1}^{Q} a_j t^{j} \right)
\]
Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
        \left\langle \epsilon , \gamma \right\rangle
\]
The inner product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
depend on $t$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \exp(a_0) \left\langle \gamma , \gamma \right\rangle
\]
so we can estimate $a_0$ as
\begin{equation}
    \label{eq:ddmesta0}
    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
\end{equation}

\section{Estimating the \lowercase{$a_{i,j}$} of $P$ components}

We examine how the mixture model influences the estimation of the $a_{i,j}$ in
Eq.~\ref{eq:polyphaseexpmix}.
Consider a mixture of $P$ components.
If we define the weighted signal sum
%
\[
    g(t) = \sum_{i=1}^{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}^{P} f_{i}(t)
\]
%
and substitute $g$ for $f$ in Eq.~\ref{eq:ddm:weighted:sig:derivative} we obtain
%
\begin{multline}
    \label{eq:mixest}
    \sum_{i=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}}
    \frac{df_{i}}{dt}(t)dt =
    0
    = \\ 
    \sum_{i=1}^{P} \left(
    \sum_{j=1}^{Q} j a_{i,j} 
    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
    + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle \right)
\end{multline}
%
From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
\right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
are small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
can simply estimate the parameters $a_{i^{\ast},j}$ using
\[
    \sum_{j=1}^{Q} j a_{{i^{\ast}},j} 
    \left\langle \mathcal{T}^{j-1} x_{i^{\ast}} , \overline{\psi}_{r} \right\rangle
    = -\left\langle x_{i^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\]
for $1 \leq r \leq R$. To compute $a_{i^{\ast},0}$ we simply use
\[
    \gamma_{i^{\ast}}(t) = \exp \left( \sum_{j=1}^{Q} a_{i^{\ast},j} t^{j} \right)
\]
in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.

\section{Designing the $\psi_{r}$}
\label{sec:designingatoms}
%
\begin{figure*}[t]
    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
spectrum characteristics of the continuous 4-term Nuttall window, the digital
prolate window with $W=0.008$, and the continuous approximation to the digital
prolate window.}
\end{figure*}
%
In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
$T$ the sample period in seconds. In this way, the chosen atoms $\psi_{\omega}(t)$ 
are the products of the elements of the Fourier basis and an appropriately
chosen window $w$ that is once differentiable and finite, i.e.,
%
\[
    \psi_{\omega}(t) = w(t) \exp(-\sqrt{-1} \omega t)
\]
%
Defining $N = \frac{L_{t}}{T}$ and $\omega = 2
\pi \frac{r}{N}$, the approximate
inner product is then
%
\[
    \left\langle x , \psi_{\omega} \right\rangle \approx 
    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
\]
%
i.e., the definition of the DFT of a windowed signal%
\footnote{%
    Notice however that this is an approximation of the inner product and should
    not be interpreted as yielding the Fourier series coefficients of a properly
    sampled signal $x$ periodic in $L_{t}$. This means that other
    evaluations of the inner product that yield more accurate results are
    possible. For example, the analytic solution is possible if $x$ is assumed
    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
    general analytic).  In this case the samples of $x$ are convolved with the
    appropriate interpolating sinc functions and the integral of this function's
    product with $\psi$ is evaluated.
}. %
The DFT is readily interpreted as a bank of bandpass filters centred at
normalized frequencies%
\footnote{%
In this article as in much of the literature on signal processing the index $r$
of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
\frac{r}{N}$ will be referred to as its bin number.
}
$\frac{r}{N}$ and with frequency response described by the Fourier transform of
modulated $w$ \cite{allen1977unified}. Therefore choosing $\psi$ amounts to a
filter design problem under the constraints that the impulse response of the
filter be differentiable in $t$ and finite. To minimize the influence of all but
one component, granted the components's energy concentrations are sufficiently
separated in frequency, we desire impulse responses whose magnitude response
gives maximum out-of-band rejection or equivalently, windows whose Fourier
transform exhibits the lowest sidelobes.

@@

\section{Differentiable approximations to windows}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{ddm_snr_win_comp}.eps}}
\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
    phase sinusoids averaged over $K_{1}=\Ksnr{}$ trials using atoms generated from
    various windows. \textit{C} is the Cram\'{e}r-Rao
lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continuous
5-cosine-term approximation to a digital prolate window as described in
Sec.~\ref{sec:designexample}.}
\end{figure*}
%
A differentiable approximation to a symmetrical window can be designed in a
straightforward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
is shown how to design optimal windows of length $N$ samples using a linear
combination of $M$ harmonically related cosines
\begin{equation}
    w(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
\mathcal{R}(\frac{n}{N})
\end{equation}
where $\mathcal{R}$ is the \textit{rectangle function}. This function is
discontinuous
at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
\[
\sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
\]

Rather than design based on an optimality criterion, such as the height of the
highest sidelobe \cite{rabiner1970approach}, a once-differentiable approximation
to an existing window $v$ is desired. To do this, we choose the $b_{k}$ so that
the window $w$'s squared approximation error to $v$ is minimized while having
$w(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{ b^{\ast}_{k} \}$ to the
mathematical program
\begin{equation}
    \label{eq:searchcontwinprogram}
    \text{minimize}
    \sum_{n=0}^{N-1} ( v(n) 
        - \sum_{k=0}^{M-1} b_{k} \cos(2 \pi k \frac{n}{N}))^{2}
\end{equation}
\[
    \text{subject to} \\
    \sum_{k=0}^{M-1} b_{k} \cos(\pi k ) = 0
\]
which can be solved using constrained least-squares; a standard numerical
linear algebra routine \cite[p.~585]{golub1996matrix}.

\section{A continuous window design example}
\label{sec:designexample}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{comp_offset_chirp_est_err_params}.eps}}
\caption{\label{fig:mixwincomp} The mean squared estimation error for each
    parameter in an analysis of two components in mixture. A set of
    $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
    maximum bin differences $0 \leq d < \Doffset{}$, with $d$ varied in
    $\Dstep{}$ bin increments. Only local maxima are plotted for clarity. The signal power ratio
    between components is indicated with colours and the corresponding ratio in decibels is indicated in the
    plot legend. The names indicate the windows used to generate the atoms for
    estimation: \textit{N3} and \textit{N4} are the 3- and 4-cosine-term
    continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
is the continuous 5-cosine-term approximation to a digital prolate window as
described in Sec.~\ref{sec:designexample}.}
\end{figure*}
%
As a design example we show how to create a continuous approximation of a digital
prolate spheroidal window.

@@

>>>>

\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subfig} % or can use subcaption package
\usepackage{color}
\usepackage{cite}
\usepackage{float}

@@

% Flowchart drawing stuff
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning, calc}
\tikzstyle{startstop} = [rectangle,draw=black,text centered]%, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=0cm, text
centered, draw=black, text width=3cm]
\tikzstyle{emptybox} = []
\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]
\tikzstyle{noarrow} = [thick,-,>=stealth]

@@

%---------------TWO-AUTHOR HEADER STARTS (uncomment below if your paper has two authors)-----------------------
\twoaffiliations{
\paperauthorA \,}
{\href{http://www.cirmmt.org/}{%Sound Processing and Control Laboratory
        SPCL %
        \sthanks{Sound Processing and Control Laboratory} \\%
%        Centre for Interdisciplinary Research in Music Media and Technology
        CIRMMT %
        \sthanks{Centre for Interdisciplinary Research in Music Media and Technology}%
    }
\\ McGill University %
\\ Montreal, Quebec, Canada \\
{\tt \href{mailto:nicholas.esterer@mail.mcgill.ca}{nicholas.esterer@mail.mcgill.ca}}
}
{\paperauthorB \,}
{\href{http://www.cirmmt.org/}{%Sound Processing and Control Laboratory
        SPCL \\%
%        \sthanks{Sound Processing and Control Laboratory} \\%
%        Centre for Interdisciplinary Research in Music Media and Technology
        CIRMMT %
%        \sthanks{Centre for Interdisciplinary Research in Music Media and Technology}%
    } %
\\ McGill University %
\\ Montreal, Quebec, Canada \\
\tt %
\href{mailto:philippe.depalle@mcgill.ca}{philippe.depalle@mcgill.ca}}

@@

The sinusoidal model approximating signal $s$ typically considered is
%
\begin{equation}
    \label{eq:polyphaseexp}
    \tilde{s}(t) = \exp(a_0 + \sum_{q=1}^{Q} a_{q} t^q) + \eta(t)
\end{equation}
where $\tilde{s}$ is the approximating signal, $t$ the variable of time, the
$a_{q} \in \mathbb{C}$ coefficients of the argument's polynomial, and $\eta(t)$
white Gaussian noise.
%
Although this technique can be extended to describe a single sinusoid of
arbitrary complexity simply by increasing $Q$, it remains essential to consider
signals featuring a sum of $P$ such components, whether they represent the harmonic structure of a musical sound or the union of partials resulting from a mixture of multiple signal sources (e.g., recordings of multiple speakers or performers),  i.e., 
%
\begin{equation}
    \label{eq:polyphaseexpmix}
    x(t) = \sum_{p=1}^{P} x_{p}(t) + \eta(t)
\end{equation}
%
with
%
\begin{equation}
    x_{p}(t) = \exp(a_{p,0} + \sum_{q=1}^{Q} a_{p,q} t^q)
\end{equation}
%
As regards the design and evaluation of signal-derivatives analysis techniques,
previous work has generally assumed signals containing a single component, i.e.,
$P$ = 1 or assumed the influence of other components to be negligible. Later we
will refine when this assumption can be made. In \cite{hamilton2012comparisons}
the authors provide a comprehensive evaluation of various signal-derivatives
analysis methods applied to a single-component signal. In
\cite{robel2002estimating} the extent to which two components in mixture can
corrupt estimations of the frequency slope ($\Im\{a_{0,2}\}$ and
$\Im\{a_{1,2}\}$) is investigated in the context of the reassignment method, one
of the signal-derivatives techniques, but the corruption of the other
parameters is not considered.

In this paper, we revisit the quality of signal-derivatives estimation of
\textit{all} the $a_{q}$ when analyzing a \textit{mixture} of components. We focus on
the DDM \cite{betser2009sinusoidal} analysis method for its convenience as it
can simply be considered as an atomic decomposition (see
Sec.~\ref{sec:estimating_aj}), and does not require computing derivatives
of the signal to be analysed.

The DDM does, however, require a once-differentiable analysis window. As we are
interested in windows with lower sidelobes in order to better estimate
parameters of sinusoidal chirp signals in mixture, we seek windows that
combine these two properties. For this, a technique to design
once-differentiable approximations to arbitrary symmetrical windows is proposed
and presented along with a design example for a high-performance window. Finally
we evaluate the performance of various once-differentiable windows in estimating
the $a_{q}$.

\section{Estimating the parameters \lowercase{$a_{q}$}}
\label{sec:estimating_aj}
We will now show briefly how the DDM can be used to estimate the $a_{q}$. Based on
the theory of distributions \cite{schwartz1959theorie}, the DDM
makes use of ``test
functions'' or atoms $\psi$. These atoms must be once differentiable with
respect to time variable $t$ and be non-zero only on a finite interval
$[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define the inner product
%
\begin{equation}
    \label{eq:ddm:inner:prod:def}
    \left\langle x , \psi \right\rangle = 
    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
\end{equation}
%
and the operator 
%
\begin{equation}
\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
\end{equation}
%
Consider the weighted signal
%
\begin{equation}
    f(t) = x(t) \overline{\psi}(t)
\end{equation}
%
differentiating with respect to $t$ we obtain
%
\begin{multline}
    \label{eq:ddm:weighted:sig:derivative}
    \frac{df}{dt}(t) = 
    \frac{dx}{dt}(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t) = \\
    \left( \sum_{q=1}^{Q} q a_{q} t^{q-1} \right) x(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t)
\end{multline}
%
Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
$\frac{df}{dt}(t)$ we obtain
%
\begin{multline}
    \int_{-\infty}^{\infty}\frac{df}{dt}(t)dt = \\
    \sum_{q=1}^{Q} q a_{q} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{q-1} x(t) \overline{\psi}(t) dt
    + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
\end{multline}
%
or, using the operator $\mathcal{T}^{\alpha}$,
%
\begin{equation} 
    \sum_{q=1}^{Q} q a_{q} 
    \left\langle \mathcal{T}^{q-1} x , \overline{\psi} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
\end{equation}
%

Estimating coefficients $a_{q}$, ${1 < q \leq Q}$,
simply requires $R$ atoms with $R \geq Q$ to solve the linear system of
equations
\begin{equation}
    \label{eq:ddmsyseq}
    \sum_{q=1}^{Q} q a_{q} 
    \left\langle \mathcal{T}^{q-1} x , \overline{\psi}_{r} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dt} \right\rangle
\end{equation}
for $1 \leq r \leq R$.

To estimate $a_0$ we rewrite the signal we are analysing as
\begin{equation}
    x(t) = \exp(a_0) \gamma(t) + \epsilon (t)
\end{equation}
where $\epsilon (t)$ is the error signal, the part of the signal that is not explained
by our model, and $\gamma (t)$ is the part of the signal
whose coefficients have already been estimated, i.e.,
\begin{equation}
    \gamma(t) = \exp \left( \sum_{q=1}^{Q} a_{q} t^{q} \right)
\end{equation}
Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
\begin{equation}
    \left\langle x , \gamma \right\rangle
    =
    \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
        \left\langle \epsilon , \gamma \right\rangle
\end{equation}
The inner product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
depend on $t$, we have
\begin{equation}
    \left\langle x , \gamma \right\rangle
    =
    \exp(a_0) \left\langle \gamma , \gamma \right\rangle
\end{equation}
so we can estimate $a_0$ as
\begin{equation}
    \label{eq:ddmesta0}
    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
\end{equation}

As will be seen in subsequent sections, the DDM typically involves taking the
discrete Fourier transform (DFT) of the signal windowed by both an everywhere once-differentiable function of
finite support (e.g., the Hann window) and this function's derivative. A small
subset of atoms corresponding to the peak bins in the DFT are used in
Eq.~\ref{eq:ddmsyseq} to solve for the parameters $a_{q}$.

\section{Estimating the \lowercase{$a_{p,q}$} of $P$ components}

We examine how the mixture model influences the estimation of the $a_{p,q}$ in
Eq.~\ref{eq:polyphaseexpmix}.
Consider a mixture of $P$ components.
If we define the weighted signal sum
%
\begin{equation}
    g(t) = \sum_{p=1}^{P} x_{p}(t) \overline{\psi}(t) = \sum_{p=1}^{P} f_{p}(t)
\end{equation}
%
and substitute $g$ for $f$ in Eq.~\ref{eq:ddm:weighted:sig:derivative} we obtain
%
\begin{multline}
    \label{eq:mixest}
    \sum_{p=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}}
    \frac{df_{p}}{dt}(t)dt =
    0
    = \\ 
    \sum_{p=1}^{P} \left(
    \sum_{q=1}^{Q} q a_{p,q} 
    \left\langle \mathcal{T}^{q-1} x_i , \overline{\psi} \right\rangle
    + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle \right)
\end{multline}
%
From this we see if $\left\langle \mathcal{T}^{q-1} x_i , \overline{\psi}_{r}
\right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
are small for all but $p = p^{\ast}$ and a subset of $R$ atoms, we
can simply estimate the parameters $a_{p^{\ast},q}$ using
\begin{equation}
    \sum_{q=1}^{Q} q a_{{p^{\ast}},q} 
    \left\langle \mathcal{T}^{q-1} x_{p^{\ast}} , \overline{\psi}_{r} \right\rangle
    = -\left\langle x_{p^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\end{equation}
for $1 \leq r \leq R$. To compute $a_{p^{\ast},0}$ we simply use
\begin{equation}
    \gamma_{p^{\ast}}(t) = \exp \left( \sum_{q=1}^{Q} a_{p^{\ast},q} t^{q} \right)
\end{equation}
in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.

\section{Designing the $\psi_{r}$}
\label{sec:designingatoms}
%
\begin{figure*}[t]
    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
spectrum characteristics of the continuous 4-term Nuttall window, the digital
prolate window with $W=0.008$, and the continuous approximation to the digital
prolate window.}
\end{figure*}
%
In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
the DFT on a signal $x$ that is properly sampled
and so can be evaluated at a finite number of time-points $nT$ with $n \in [0,N-1]$ and
$T$ the sample period in seconds. In this way, the chosen atoms $\psi_{\omega}(t)$ 
are the products of the elements of the Fourier basis and an appropriately
chosen window $w$ that is once differentiable and finite, i.e.,
%
\begin{equation}
    \label{eq:fourieratom}
    \psi_{\omega}(t) = w(t) \exp(-j \omega t)
\end{equation}
%
Defining $N = \frac{L_{t}}{T}$ and angular frequency at bin $r$ as $\omega = 2
\pi \frac{r}{N}$, the approximate inner product is then
%
\begin{equation}
    \label{eq:approxinnerprod}
    \left\langle x , \psi_{\omega} \right\rangle \approx 
    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi j r \frac{n}{N}) 
\end{equation}
%
i.e., the definition of the DFT of a windowed signal%
\footnote{%
    Notice however that this is an approximation of the inner product and should
    not be interpreted as yielding the Fourier series coefficients of a properly
    sampled signal $x$ periodic in $L_{t}$. This means that other
    evaluations of the inner product that yield more accurate results are
    possible. For example, the analytic solution is possible if $x$ is assumed
    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
    general analytic).  In this case the samples of $x$ are convolved with the
    appropriate interpolating sinc functions and the integral of this function's
    product with $\psi$ is evaluated.
}. %
The DFT is readily interpreted as a bank of bandpass filters centred at
normalized frequencies%
%\footnote{%
%In this article as in much of the literature on signal processing the index $r$
%of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
%\frac{r}{N}$ will be referred to as its bin number.
%}
$\frac{r}{N}$ and with frequency response described by the Fourier transform of
modulated $w$ \cite{allen1977unified}. Therefore choosing $\psi$ amounts to a
filter design problem under the constraints that the impulse response of the
filter be differentiable in $t$ and finite. To minimize the influence of all but
one component, granted the components's energy concentrations are sufficiently
separated in frequency, we desire impulse responses whose magnitude response
gives maximum out-of-band rejection or equivalently, windows whose Fourier
transform exhibits the lowest sidelobes.

@@

\section{Differentiable approximations to windows}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{ddm_snr_win_comp}.eps}}
\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
    phase sinusoids averaged over $K_{1}=\Ksnr{}$ trials using atoms generated from
    various windows. \textit{C} is the Cram\'{e}r-Rao
lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continuous
5-cosine-term approximation to a digital prolate window as described in
Sec.~\ref{sec:designexample}.}
\end{figure*}
%
A differentiable approximation to a symmetrical window can be designed in a
straightforward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
is shown how to design optimal windows of length $N$ samples using a linear
combination of $M$ harmonically related cosines
\begin{equation}
    \tilde{w}(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
\mathcal{R}(\frac{n}{N})
\end{equation}
where $\mathcal{R}$ is the \textit{rectangle function}. This function is
discontinuous
at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
\begin{equation}
\sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
\end{equation}

Rather than design based on an optimality criterion, such as the height of the
highest sidelobe \cite{rabiner1970approach}, a once-differentiable approximation
to an existing window $w$ is desired. To do this, we choose the $b_{k}$ so that
the window $\tilde{w}$'s squared approximation error to $w$ is minimized while having
$\tilde{w}(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{ b^{\ast}_{k} \}$ to the
mathematical program
\begin{equation}
    \label{eq:searchcontwinprogram}
    \text{minimize}
    \sum_{n=0}^{N-1} ( w(n) 
        - \sum_{k=0}^{M-1} b_{k} \cos(2 \pi k \frac{n}{N}))^{2}
\end{equation}
\begin{equation}
    \text{subject to} \\
    \sum_{k=0}^{M-1} b_{k} \cos(\pi k ) = 0
\end{equation}
which can be solved using constrained least-squares; a standard numerical
linear algebra routine \cite[p.~585]{golub1996matrix}.

\section{A continuous window design example}
\label{sec:designexample}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{comp_offset_chirp_est_err_params}.eps}}
\caption{\label{fig:mixwincomp} The mean squared estimation error for each
    parameter in an analysis of two components in mixture. A set of
    $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
    maximum bin differences $0 \leq d < \Doffset{}$, with $d$ varied in
    $\Dstep{}$ bin increments. The signal power ratio
    between components is indicated with colours and the corresponding ratio in decibels is indicated in the
    plot legend. The names indicate the windows used to generate the atoms for
    estimation: \textit{N3} and \textit{N4} are the 3- and 4-cosine-term
    continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
is the continuous 5-cosine-term approximation to a digital prolate window as
described in Sec.~\ref{sec:designexample}.}
\end{figure*}
%
As a design example we show how to create a continuous approximation of a digital
prolate spheroidal window.

@@

\subsection{Signals with single component}
